---
title: "Activity 5"
subtitle: "MATH 216: Statistical Thinking"
format: html
echo: false
---

```{r setup, include=FALSE}
library(openintro)
library(dplyr)
library(knitr)
library(ggplot2)
```

## Activity 1: Think-Pair-Share

1. **Think**: Individually, list the sample space for the experiment of rolling a die and tossing a coin simultaneously.
2. **Pair**: Discuss with a partner to compare and refine their sample spaces.
3. **Share**: Share your combined sample space with the class and explain how you arrived at it.

<!--

**Example**: 

- **Sample Space for Die Roll and Coin Toss**: 

  $$S = \{(1, H), (1, T), (2, H), (2, T), \dots, (6, H), (6, T)\}$$

-->


## Activity 2: Quiz

1. **Question**: What is the probability of rolling a 2 on a fair six-sided die?

A) 1/6
B) 1/3
C) 1/2
D) 1/1


## Activity 4: Group Activities with Real Data

1. **Dataset**: You are given a dataset of 200 die roll outcomes
2. **Task**: 
   - Calculate the probability of rolling an even number.
   - Create a histogram of the die roll outcomes.
3. **Discussion**: Compare the empirical probability with the theoretical probability.


```{r}
# Load necessary library
library(ggplot2)
library(dplyr)

# Create a data frame
die_roll_data <- data.frame(
  outcome = sample(1:6, 200, replace = TRUE)
)

# Calculate the probability of rolling an even number
even_probability <- mean(die_roll_data$outcome %% 2 == 0)

die_roll_data %>% group_by(outcome) %>% summarize(Count = n()) %>% knitr::kable()

# Create a histogram
ggplot(die_roll_data, aes(x = outcome)) +
  geom_histogram(binwidth = 1, fill = "blue", color = "black") +
  scale_x_continuous(breaks = c(1:6)) +
  labs(title = "Histogram of Die Roll Outcomes", x = "Outcome", y = "Frequency")
```

