---
title: "Activity 2"
subtitle: "MATH 216: Statistical Thinking"
format: html
---

```{r setup, include=FALSE}
library(openintro)
library(dplyr)
library(knitr)
data(hsb2)
```

### **Activity 1: Think-Pair-Share**

1. **Think:** Reflect on a real-world example where sampling bias might occur (e.g., political polls, health surveys).
2. **Pair:** Discuss your example with a partner and identify potential sources of bias.
3. **Share:** Share your findings with the class and propose ways to mitigate the bias.


### **Activity 2: Live Quiz**


1. **Question:** "How might the wording of a survey question about climate change influence responses?"

A) It has no effect.  
B) It can lead to overestimation of public concern.  
C) It can lead to underestimation of public concern.  
D) It can polarize responses.  



### **Activity 3: Interactive Data Exploration**

::: scrollable

```{r echo=FALSE}
library(tidyverse)
# Load the MASS package
library(MASS)

# Load the crabs dataset
data(crabs)

# Display the first few rows of the dataset
crabs %>% head() %>%  knitr::kable()
```

:::

```{r echo=FALSE}
ggplot(crabs, aes(x = CL, fill = sex)) + 
  geom_histogram(binwidth = 5) + 
  facet_wrap(~sex) + 
  scale_fill_manual(values = c("maroon", "gold")) +
  labs(title = "Carpace lengtgh for Male and Female Leptograpsus Crabs") +
  theme_minimal()
```

1. **Question:** What do you see on the above plots? .




### **Activity 4: Quiz**

1. **Question:** "Experiment or Observational Study? To examine whether farm-grown salmon contain more omega-3 oils if water is more acidic, we collect samples of salmon and water from multiple fish farms to see if the two variables are related." Explain

A) Experiment.  
B) Observational Study.  
C) Not enough information.  

