---
title: "Activity 27"
subtitle: "MATH 216: Statistical Thinking"
format: 
  live-html:
    theme:
      light: [lux, theme-light.scss]
      dark: [superhero, theme-dark.scss]
engine: knitr
toc: true
echo: false
---

{{< include _extensions/r-wasm/live/_knitr.qmd >}}


```{r setup, include=FALSE}
library(openintro)
library(dplyr)
library(knitr)
library(ggplot2)
library(car)
library(BSDA)
```

### Activity 1: Quick Hypothesis Check  

**Scenario**: A company claims their meditation app reduces stress (median stress score < 20). 12 users' scores:  

`data <- c(18, 22, 19, 17, 25, 16, 21, 19, 20, 18, 23, 17)`  

**Tasks**:  

1. Calculate test statistic $S$ (number of values < 20)  
2. Write null hypothesis ($H_0: m \geq 20$)  
3. Calculate binomial probability for $S$ successes  
4. R code: `SIGN.test(data, md=20, alternative="less")`  

```{webr}

```


### Activity 2: P-Value Understanding  

**Question**: For n=15 non-zero differences with 12 positive signs (testing $H_1: m > m_0$), which formula calculates the one-tailed p-value?  

**Options**:  

A) $P(X \leq 12)$  
B) $P(X \geq 12)$  
C) $2 \times P(X \geq 12)$  
D) $P(X = 12)$  


### Activity 3: Test Statistic Calculation  

**Data**: 10 paired observations with 7 positive differences, 1 negative, 2 zeros.  

**Question**: What is the value of the test statistic $S$?  


### Activity 4: R Code Interpretation  

```{r}  
SIGN.test(x = c(3,5,-2,0,1), md=2, alternative="two.sided")  
```  

**Question**: What is being tested?  


### P-Value Discussion Key Points:  

<blockquote>

1. Under $H_0$, probability of "+" signs follows binomial$(n,0.5)$  

2. For $S$ observed "+" signs:  

   - Left-tailed: $P(X \leq S)$  
   - Right-tailed: $P(X \geq S)$  
   - Two-tailed: $2 \times \min[P(X \leq S), P(X \geq S)]$  
   
3. In R, `SIGN.test()` automatically handles:  

   - Exclusion of zero differences  
   - Normal approximation for large n  
   - Exact binomial p-value for small n  

</blockquote>

### Activity 5: Full Analysis  

**Scenario**: 14 patients tried a diet. Weight changes:  

`differences <- c(-2, -1, 0, -3, -2, -1, -4, 0, -3, -2, -1, -2, 0, -1)`  

**Tasks**:  

1. State $H_0$ ($m \geq 0$) vs $H_1$ ($m < 0$)  
2. Calculate $S$ = number of positive differences 
3. Exact p-value = `pbinom(S, 12, 0.5)` 
4. Conclusion at α=0.05: 



