---
title: "Activity 11"
subtitle: "MATH 216: Statistical Thinking"
format: html
echo: false
---

```{r setup, include=FALSE}
library(openintro)
library(dplyr)
library(knitr)
library(ggplot2)
```


## Activity 1: Think-Pair-Share

1. **Think:** Reflect on the following question:  

   - *Why is the probability of a continuous random variable taking on a specific value always zero?*  
   - *How does the area under the PDF curve relate to probability?*

2. **Pair:** Discuss your thoughts with a partner and come up with a joint explanation.

3. **Share:** Share your insights with the class, focusing on how the properties of PDFs differ from those of discrete probability mass functions.


\vspace*{1in}

## Activity 2: Quiz

- **Question:** Suppose $X$ is uniformly distributed between $a = 2$ and $b = 8$.  

  - What is the probability that $X$ falls between 3 and 5?  
  - Calculate the mean and variance of $X$.

**Instructions:** Use the formula for the uniform distribution: 

- $P(c \leq X \leq d) = \frac{d-c}{b-a}$  
- $\mu = \frac{a+b}{2}$  
- $\sigma^2 = \frac{(b-a)^2}{12}$

\vspace*{1in}


## Activity 3: Data Exploration

```{r}
#| echo: true
library(ggplot2)

# Generate uniform distribution data
set.seed(123)  # For reproducibility
a <- 0
b <- 6
x <- runif(1000, a, b)

# Create a data frame
data <- data.frame(x = x)

# Plot using ggplot2
ggplot(data, aes(x = x)) +
  geom_histogram(aes(y=after_stat(density)),bins = 30,fill="lightblue",color="black") +
  geom_function(fun=dunif, args=list(min = a, max = b), color="red", linewidth=1.5) +
  labs(
    title = "Uniform Distribution PDF",
    x = "X",
    y = "Density"
  ) +
  theme_minimal()
```

**Task:** 

- Modify the values of $a$ and $b$ to see how the distribution changes.  
- Calculate the mean and variance of the generated data and compare them to the theoretical values.

\vspace*{1in}


## Activity 4: Probability Calculations

**Prompt:** An unprincipled used-car dealer sells a car to an unsuspecting buyer, even though the dealer knows that the car will have a major breakdown within the next 6 months. The dealer provides a warranty of 45 days on all cars sold. Let $x$ represent the length of time until the breakdown occurs. Assume that x is a uniform random variable with values between 0 and 6 months.

a. Calculate and interpret the mean and standard deviation of $X$.

\vspace*{0.5in}


b. Graph the probability distribution of $X$ , and show the mean on the horizontal axis. Also show one and two-standard-deviation intervals around the mean.

\vspace*{0.5in}


c. Calculate the probability that the breakdown occurs while the car is still under warranty.




