---
title: "Activity 30"
subtitle: "MATH 216: Statistical Thinking"
format: 
  live-html:
    theme:
      light: [lux, theme-light.scss]
      dark: [superhero, theme-dark.scss]
engine: knitr
toc: true
echo: false
---

{{< include _extensions/r-wasm/live/_knitr.qmd >}}


```{r setup, include=FALSE}
library(openintro)
library(dplyr)
library(knitr)
library(ggplot2)
library(car)
library(BSDA)
```


### Activity 1: Quiz 

- What is the null hypothesis for the Mann-Whitney U test?  

  A) The medians are equal  
  B) The means are equal  
  C) The variances are equal  
  D) The distributions are identical  

### Activity 2: Group Height Analysis

**Task:** Compare heights using Wilcoxon Rank Sum:  

```{r}
group1 <- c(160,165,170,155,168)
group2 <- c(172,168,175,180,165)
wilcox.test(group1, group2)
```

\vspace*{1in}


### Activity 3: Treatment Recovery Case Study

**Solution:** 

```{r}
treatment_a <- c(10,12,14,11,13)
treatment_b <- c(15,14,16,17,12)
wilcox.test(treatment_a, treatment_b, paired=TRUE)
```

\vspace*{1in}


### Activity 4: Exam Scores Analysis (From Slides)


```{r}
online <- c(78,82,83,87,75,43,78,42,94,47,98,90,97,81)
traditional <- c(83,82,92,100,74,90,44,84,77,89,70,34)
wilcox.test(online, traditional)
```


